---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, cache = TRUE,
  comment = "# ",
  fig.path = "figures/README-"
)
```


#lindia

lindia is an extention to ***ggplot2*** to allow easy plotting of linear diagnostic plots. The following demonstrates basic plotting features of `lindia`. All functions in `lindia` takes in lm object and return linear diagnostic plots in types of `ggplot`.

```{r, warning = F, message = F}
library(MASS)
library(ggplot2)
library(lindia)
data(Cars93)
cars_lm <- lm(Rev.per.mile ~ Passengers + Length + RPM, data = Cars93)
gg_resfitted(cars_lm)
```

All themes in `lindia` plots can be overwritten by a call to `ggplot::theme()`.


```{r, warning = F, message = F}
gg_reshist(cars_lm) + theme_bw()
```

Please note that `lindia` does not provide ***all*** diagnostic plots necessary for checking linear model assumptions. Refer to ggpairs to check if multicolinearity assumption has been violated.

#Overview
Followed are functions implemented in `lindia`:

+ `gg_reshist()`: plotting the histogram of distribution of residuals
+ `gg_resfitted()`: residual plot of residuals by fitted value
+ `gg_resX()`: a list of residual plots of all predictors by fitted value (continuous variables only for now. Categorical and interaction terms are developing.)
+ `gg_qqplot()`: Normaility quantile-quantile plot (QQPlot) with qqline overlayed on top
+ `gg_boxcox()`: boxcox graph with optimal transformation labeled on graph
+ `gg_scalelocation()`: scale-location plot (also called spread-location plot).
+ `gg_resleverage()`: residual vs. leverage plot. (cook distance indicators not implemented for now)
+ `gg_diagnose()`: all diagnostic plots being layed out on a grid (not functional yet).

Functions that maybe implemented:

+ `diagnames()`: returns a vector of names of all diagnostic plots available for a given lm object


#Functions in Lindia

###gg_reshist

Plot distribution of residuals in histograms. Number of bins picked by default.
```{r, warning = F, message = F}
gg_reshist(cars_lm)
```

Can also specify number of bins using `bins` argument:
```{r, warning = F, message = F}
gg_reshist(cars_lm, bins = 20)
```

###gg_resfitted
Plots residual against fitted value.
```{r, warning = F, message = F}
gg_resfitted(cars_lm)
```


###gg_boxocx

Plots boxcox graph of given lm object, with labels showing optimal transforming power. Can hide labels by setting `showlambda` to `FALSE`.
```{r, warning = F, message = F}
gg_boxcox(cars_lm)
```

#How to Install
+ From Github:  `devtools::install_github("yeukyul/lindia")`


