---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, cache = TRUE,
  comment = "# ",
  fig.path = "figures/README-"
)
```


#lindia

lindia is an extention to ***ggplot2*** to allow easy plotting of linear diagnostic plots. The following demonstrates basic plotting features of `lindia`. All functions in `lindia` takes in lm object and return linear diagnostic plots in types of `ggplot`.

```{r, warning = F, message = F}
library(MASS)
library(ggplot2)
library(lindia)
data(Cars93)
cars_lm <- lm(Rev.per.mile ~ Passengers + Length + RPM, data = Cars93)
gg_resfitted(cars_lm)
```

All themes in `lindia` plots can be overwritten by a call to `ggplot::theme()`.


```{r, warning = F, message = F}
gg_reshist(cars_lm) + theme_bw()
```


#Functions in Lindia

###gg_reshist

Plot distribution of residuals in histograms. Number of bins picked by default.
```{r, warning = F, message = F}
gg_reshist(cars_lm)
```

Can also specify number of bins using `bins` argument:
```{r, warning = F, message = F}
gg_reshist(cars_lm, bins = 20)
```

###gg_resfitted
Plots residual against fitted value.
```{r, warning = F, message = F}
gg_resfitted(cars_lm)
```


#How to Install
+ From Github:  `devtools::install_github("yeukyul/lindia")`


